---
title: "Animation plots"
output: html_document
---

```{r prep}
library(pacman)
p_load(dplyr, ggplot2, gganimate)

df_tracking <- readRDS("output_data/df_tracking_0705.rds")
df_event <- readRDS("../Maria_thesis/data/df_event.rds")
df_event <- df_event %>% 
  distinct(matchId, match, season, date)

features <- readRDS("output_data/features_final_1105.rds")
predictions_df <- readRDS("predictions_df.rds")

predictions_df <- predictions_df %>%
  mutate(pred_error = pred-perf_score) %>%  
  mutate(abs_pred_error = abs(pred-perf_score))

players <- read.csv("output_data/players.csv")

df_tracking <- df_tracking %>% 
#  dplyr::select(-ID) %>% 
  left_join(players, by="playerId") %>%  
  rename(PlayerID = ID) %>%  
  mutate(PlayerID = ifelse(is.na(PlayerID), "O", PlayerID)) %>%  
  mutate(PlayerID = ifelse(contestantId != "9qsmopgutr7ut5g6workk8w4i", shirtNumber, PlayerID))

predictions_df <- predictions_df %>%
  mutate(pred_error_group = ifelse(abs_pred_error < 5, "Very low prediction error", 
                                   ifelse(abs_pred_error >= 5 & abs_pred_error <10, "Low prediction error", 
                                          ifelse(abs_pred_error >= 10 & abs_pred_error < 20, "Medium prediction error",
                                                 ifelse(abs_pred_error >= 20 & abs_pred_error < 50, "High prediction error",
                                                        ifelse(abs_pred_error >=50, "Very high prediction error", ""))))))

predictions_df <- predictions_df %>%
  mutate(segment_start = ifelse(ball_start_x<=1750, "Defence", 
                                ifelse(ball_start_x>1750 & ball_start_x<3500, "Midfield", 
                                       "Offense")))
```

# Animation plots  

## Highest performance value - defence
```{r}
phase_id_input <- 3430
source("source/animation_func.R")
animated_p
anim_save("high_performance_defence_3430.gif")
```

## High performance value - offense
```{r}
phase_id_input <- 28578
source("source/animation_func.R")
animated_p
anim_save("high_performance_offense_28578.gif")
```


## Low performance value - defence
```{r}
phase_id_input <- 9480
source("source/animation_func.R")
animated_p
anim_save(paste0("Low_perf_def", phase_id_input, ".gif"))
```

## Low performance value - offense
```{r}
phase_id_input <- 45587
source("source/animation_func.R")
animated_p
anim_save(paste0("Low_perf_def", phase_id_input, ".gif"))
```


## Lowest value dist x
```{r}
phase_id_input <- 10650
source("source/animation_func.R")
animated_p
anim_save(paste0("lowest_val_dist_x_", phase_id_input, ".gif"))
```


## Highest value dist x
```{r}
phase_id_input <- 6658
source("source/animation_func.R")
animated_p
anim_save(paste0("highest_val_dist_x_", phase_id_input, ".gif"))
```


## Lowest value dist y
```{r}
phase_id_input <- 4001
source("source/animation_func.R")
animated_p
anim_save(paste0("lowest_val_dist_y_", phase_id_input, ".gif"))
```

## Highest value dist y
```{r}
phase_id_input <- 9631
source("source/animation_func.R")
animated_p
anim_save(paste0("highest_val_dist_y_", phase_id_input, ".gif"))
```

## Highest value of convex hull
```{r}
phase_id_input <- 1291	
source("source/animation_func.R")
animated_p
anim_save(paste0("high_convex_hull", phase_id_input, ".gif"))
```

## Lowest value of convex hull
```{r}
phase_id_input <- 18392
source("source/animation_func.R")
animated_p
anim_save(paste0("low_convex_hull", phase_id_input, ".gif"))
animated_p
```

## High value of convex hull in defence (performance score = 7.74)
```{r}
phase_id_input <- 8172
source("source/animation_func.R")
animated_p
anim_save(paste0("high_convex_hull_defence", phase_id_input, ".gif"))
```

## High negative prediction error (-63.33)
```{r}
phase_id_input <- 39404
source("source/animation_func.R")
animated_p
anim_save(paste0("high_neg_pred_error", phase_id_input, ".gif"))
```

## High positive prediction error (76.49)
```{r}
phase_id_input <- 6983
source("source/animation_func.R")
animated_p
anim_save(paste0("high_pos_pred_error", phase_id_input, ".gif"))
```

## Smallest prediction error in offensive segment (0.00788325)
```{r}
phase_id_input <- 32901
source("source/animation_func.R")
animated_p
anim_save(paste0("low_abs_pred_error_off_segment", phase_id_input, ".gif"))
```

## Biggest prediction error in offensive segment (76.49228)
```{r}
phase_id_input <- 33006
source("source/animation_func.R")
animated_p
anim_save(paste0("high_abs_pred_error_off_segment", phase_id_input, ".gif"))
```


## EXPLORATIVE
```{r}
phase_id_input <- 17890
source("source/animation_func.R")
animated_p
anim_save("standard_situation_2.gif")
```

